Pattern Avoidance

### 2014-11-07 project2/paper/paper.tex

\begin{corollary} 
For a permutation $\pi$, $s_n(\pi)=s_n(\mathcal{F}(\pi))$. 
\end{corollary}
\begin{proof}
This result follows because the flipping lemma gives a bijection between permutations that avoid $\pi$ and permutations that avoid $\mathcal{F}(\pi)$. 
\end{proof}
\section{Terms in the sequence $s_n(312)$}
\label{312}

@@

By the flipping lemma and reversing lemmas we see that  $s_n(132)$, $s_n(213)$ and $s_n(231)$ are the sequence of Catalan numbers as well.

>>>>

\begin{corollary} 
For a permutation $\pi$, $s_n(\pi)=s_n(\mathcal{F}(\pi))$. 
\end{corollary}
\begin{proof}
This result follows because the flipping lemma gives a bijection between permutations that avoid $\pi$ and permutations that avoid $\mathcal{F}(\pi)$. 
\end{proof}

\emph{Yajit wrote this section.}

\section{Avoiding Permutations of Length Three Part I}
\label{312}

@@

By the flipping lemma and reversing lemma we see that  $s_n(132)$, $s_n(213)$ and $s_n(231)$ are the sequence of Catalan numbers as well. 
\end{proof}

\emph{Deepak wrote this section.}
